Development of Online Judge Using Contestant PC As Worker of Autograder

### 2019-06-28 src/paper.tex
add related work

In order to grade contestant submissions, online judge system has a subsystem called autograder. Contestant submissions which are source code in certain programming language will be graded by autograder system by compiling the program and executes compiled program using test-cases that have been prepared by juries or problem setter. According \cite{jordanioi}, this grading method is called black-box grading. By using autograder system, the grading process can be done automatically and juries don't have to evaluate contestant submissions manually. In order to increase the number of contestant submissions in certain amount of time, juries usually deploy autograder in many computers. In order to run autograder in many computers, the juries need to prepare many computers with the same spesification to keep the fairness of grading process.

Currently, almost every competitive programing competition use online judge system to support the competition and use many computers to run autograder in order to improve grading performance. Grading performance is defined as the number of submissions graded in certain amount of time. Even though autograder deployed in many computers, the grading performance often not enough to evaluate contestant solutions in real-time because the number of contestants is increasing. Furthermore, the number of computer to deploy autograder affect the procurement cost that juries need to be incurred. Therefore, new grading system is needed to increase grading performance without increasing procurement cost that need to be incurred.

@@

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

>>>>

In order to grade contestant submissions, online judge system has a subsystem called autograder. Contestant submissions which are source code in certain programming language will be graded by autograding system by compiling the program and executes compiled program using test-cases that have been prepared by juries or problem setter. According \cite{jordanioi}, this grading method is called black-box grading. By using autograding system, the grading process can be done automatically and juries don't have to evaluate contestant submissions manually. In order to increase the number of contestant submissions in certain amount of time, juries usually deploy autograder in many computers. In order to run autograder in many computers, the juries need to prepare many computers with the same spesification to keep the fairness of grading process.

Currently, almost every competitive programing competition use online judge system to support the competition and use many computers to run autograder in order to improve grading performance. Every computers that run autograder are called worker. Grading performance is defined as the number of submissions graded in certain amount of time. Even though autograder deployed in many computers, the grading performance often not enough to evaluate contestant solutions in real-time because the number of contestants is increasing. Furthermore, the number of computer to deploy autograder affect the procurement cost that juries need to be incurred. Therefore, new grading system is needed to increase grading performance without increasing procurement cost that need to be incurred.

@@

\section{Related Work}

There are some popular online judge system that have been used to organize competitive programming competition. Some online judge offer another additional features like discussion forum, training gate and rating system. Nowadays, most of online judge deployed as web application and use specific computer to grade contestant submissions. There are many types of competitive programming competition rules. Most of online judge only support a specific competition rules.

One of the most popular competitive programming competition is ACM-ICPC competition where the competition uses ICPC rules. In ACM-ICPC competition, contestants compete in group of three people. Every group have the same amount of problem to solve, and the score is determined by the number of solved problem and time penalty. There are many online judges that support this competitive programming rules. The most popular online judge that support this type of competition is DOMJudge. DOMJudge is very popular because it has many usefull feature, easy to use and open source.

Currently, most of online judge use autograder to evaluate contestant submissions. According to \cite{danutamalms}, autograder is a system that compiles, executes and evaluate source code. Evaluates source code manually takes three minutes while using autograder only need ten seconds. By using autograder, contestants can receive grading feedback faster and reduce the work that need to be done by juries. Basically, the autograder evaluate the source code by compiles the source code, and executes the compiled program using predefined test-cases. The output of contestant's solution program compared to the predefined test-case and then graded. This evaluation method is called black-box grading \cite{jordanioi}.

We need to consider security aspect when developing autograding system. Competitive programming contestants might submit source code that contain dangerous code. According to \cite{wasikojsurvey}, there are several attacks that can be made by contestants, such as submitting compile bomb code, submitting code that destroy autograding environment, and submitting code that access forbidden computer's resource. In order to prevent such things, autograding system must execute contestant's code in isolated environment called sandbox.

There are several ways to create isolated environment such as using virtual machine and containerization. By using virtual machine, one can create isolated operating system inside host computer. Virtual machine uses hypervisor to emulate computer hardware and run its own operating system. In Linux based operating system, there is a feature called KVM that make it possible to create hypervisor as a process in Linux \cite{wfeltervmcontainer}. We can use virtual machine to isolate the execution of contestant's code. However, by using virtual machine, we need to boot a new operating system each time we evaluate contestant's subission. This booting process takes so much computer's resource and reduces grading performance.

Another way to create isolated environment is by using container. Container is different from virtual machine. Container Container gives isolation in software level wihout hypervisor \cite{merkeldocker}. By using container, we can isolate process execution without boot a new operating system. Container works by using some Linux features such as chroot, namespace and cgroup. By using chroot, we can isolate filesystem of Linux process \cite{lessardchroot}. Container uses Linux feature called cgroup to limit process resources. By using cgroup, we can limit memory usage, CPU usage and disk IO usage of running process \cite{wfeltervmcontainer}. In order to hide other process, user, and network from a running process, container uses a Linux feature called namespace. By using namespace, we can isolate a Linux process from other process, so the running process not aware of the existance of other process. Instead of virtual machine, most of autograding system use container to isolate grading process. This method is used because it is more lighter and faster than virtual machine.

\section{Methodology}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.
